Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
methods through network metrics edits

## Caribou location data
We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Adult female caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population.

@@

### Network metrics 
We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals within and across layers, and the similarity of
different layers. To measure the role of individuals within layers, we
calculated degree centrality and graph strength. Degree centrality is the number
of direct connections an individual has to other individuals in a network layer.
Graph strength is the degree weighted by the strength of association, in this
case SRI, in each layer. Extending degree centrality, we calculated multidegree,
the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
overlap. Edge overlap is defined as the proportion of edges present in each
network layer out of all observed edges  [@Battiston_2014]. Network metrics were
calculated using the R packages `igraph` [@Csardi_2006], `asnipe`
[@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table` [@Dowle_2019].

>>>>

## Caribou location data
We used GPS location data collected from Fogo Island caribou between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Adult female caribou were immobilized and fitted with global positioning
system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
to remove all erroneous and outlier GPS fixes following
[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
proportion of marked adult females was ~10% of all adult females and ~5% of all
individuals in the herd. We assumed these individuals were randomly distributed
throughout the population.

@@

### Network metrics 
We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals within and across layers, and the similarity of
different layers. To measure the role of individuals within layers, we
calculated degree centrality and graph strength. Degree centrality is the number
of direct connections an individual has to other individuals in a network layer.
Graph strength is the degree weighted by the strength of association, in this
case SRI, in each layer. Extending degree centrality to multiple layers, we calculated multidegree,
the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
overlap. Edge overlap is defined as the proportion of edges present in each
network layer out of all observed edges  [@Battiston_2014]. Network metrics were
calculated using the R packages `igraph` [@Csardi_2006], `asnipe`
[@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table` [@Dowle_2019].
